Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-26 article.tex
Another round of edits for grammar and clarity.

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
We present a dual-modality imaging system combining laser speckle contrast imaging and phosphorescence lifetime quenching to simultaneously map cortical blood flow and oxygen tension (\pO) in mice. Phosphorescence signal localization is achieved through the use of a digital micromirror device (DMD) that allows for selective excitation of arbitrary regions of interest. By targeting both excitation maxima of the oxygen-sensitive porphyrin Oxyphor PtG4, we are able to examine the effects of excitation wavelength and penetration depth on phosphorescence lifetime. We demonstrate the ability to measure differences in \pO\ between arteries and veins and large changes during an hyperoxic challenge. We dynamically monitor blood flow and \pO\ during DMD-targeted photothrombotic occlusion of an arteriole and highlight the presence of an ischemia-induced depolarization. Chronic tracking of the ischemic lesion over seven days revealed a rapid recovery, with the targeted vessel fully reperfusing and \pO\ returning to baseline values within five days. This system has broad applications for studying the acute and chronic pathophysiology of ischemic stroke and other vascular diseases of the brain.
\end{abstract}

@@

\subsection{Imaging Instrumentation}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_schematic}a. Laser speckle contrast imaging (LSCI) of blood flow was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) illuminating the craniotomy at an oblique angle. Selection of the near-infrared laser diode wavelength was limited by the excitation and emission spectra of the oxygen-sensitive phosphorescent probe that dictated dichroic beamsplitter cutoff wavelengths. The scattered laser light was relayed to a CMOS camera (acA1300-60gmNIR, 1280 x 1024 pixels, Basler AG) with 2x magnification and acquired using custom software at 60 frames-per-second with a 5 ms exposure time.

@@

Simultaneously, laser light patterned by the DMD was delivered to the craniotomy to selectively excite the oxygen-sensitive phosphorescent probe. Wavelength has been shown to significantly affect the penetration depth and sampled volume of measurements through surface vasculature \cite{Davis:2011wj}, so two different lasers at 445 nm (200 mW, AixiZ) and 637 nm (250 mW, HL6388MG, Thorlabs) were selected to target the Soret and Q band excitation maxima of the dye \cite{Esipova:2011hi}. Each laser was used independently to collect \pO\ measurements from identical regions of interest for comparison. The 445 nm laser was gated using an acousto-optic modulator (23080-2-LTD, Neos Technologies) while the 637 nm laser was directly gated via its driver (LDD400-1P, Wavelength Electronics). Both lasers were gated to produce 20 $\mu$s pulses of light for time domain lifetime measurements with a 6\% duty cycle and 3 kHz repetition rate using an National Instruments FlexRIO FPGA (NI PXIe-7965R and NI 5781).

The modulated laser light was relayed to and reflected off a DMD for projection onto the craniotomy. A DMD is an optical semiconductor device that consists of a two-dimensional array of thousands of individually addressable mirrors that can be tilted to spatially modulate light. The DMD allows for the localization of phosphorescence measurements while maintaining the high SNR of using a point detector \cite{Ponticorvo:2010uv}. A DLP LightCrafter Evaluation Module (Texas Instruments) was modified to expose the bare DMD (DLP3000, 608 x 684 pixels, 7.6 $\mu$m pitch) for illumination. The projected DMD pattern was co-registered with the LSCI camera via an affine image transformation (Fig.~\ref{fig:system_schematic}b). This allowed for the selection of arbitrarily-shaped regions of interest using speckle contrast imagery for reference. The resulting binary masks were then transformed into DMD coordinate space and uploaded onto the device via its USB-based API. Each pattern was then projected sequentially onto the exposed brain tissue to selectively excite the phosphorescent probe for \pO\ measurements.

The emitted phosphorescence was separated from the excitation light and LSCI laser using a pair of dichroic beamsplitters (650 nm, ZT640rdc, Chroma Technology and 750 nm, FF750-SDi02, Semrock) and a bandpass filter (775$\pm$26 nm, 84-106, Edmund Optics) and relayed to a photomultiplier tube for detection (H7422P-50, Hamamatsu Photonics). The analog signal was digitized at 100 MHz and accumulated by the FPGA for averaging, after which it was transferred to the host computer and written to file. The maximum pattern projection rate and temporal resolution of the \pO\ measurements were limited by the averaging of the phosphorescent decays. In order to balance SNR and speed, patterns were displayed at 10 Hz with 200 decays collected during each projection. While faster pattern rates were possible (e.g. 50 Hz with 40 decays averaged), the reduction in averaging negatively affected the quality of the recorded decays.

@@

\subsection{Animal Preparation}
Mice (CD-1, male, 25-30 g, Charles River) were anesthetized with medical air vaporized isoflurane (2\%) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts). Arterial oxygen saturation, heart rate, and breath rate were monitored via pulse oximetry (MouseOx, Starr Life Sciences). After induction, mice were placed supine in a stereotaxic frame (Narishige Scientific Instrument Lab) and administered carprofen (5 mg/kg, subcutaneous) and dexamethasone (2 mg/kg, intramuscular) to reduce inflammation of the brain during the craniotomy procedure. The scalp was shaved and resected to expose skull between the bregma and lambda cranial coordinates. A thin layer of cyanoacrylate (Vetbond, 3M) was applied to exposed skull to facilitate the adhesion of dental cement during a later step. A 3-4 mm diameter portion of the skull was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) under regular artificial cerebrospinal fluid (sterile, buffered pH 7.4) perfusion. A 5-8 mm round cover glass (\#1.5, World Precision Instruments) was placed over the exposed brain with a layer of artificial cerebrospinal fluid between the two. While applying gentle pressure to the cover glass, a dental cement mixture was deposited along the perimeter, bonding it to the surrounding skull. This process created a sterile, air-tight seal around the craniotomy and allowed for restoration of intracranial pressure. A final layer of cyanoacrylate was applied over the dental cement to further seal the cranial window. Animals were allowed to recover from anesthesia and monitored for cranial window integrity and normal behavior for two weeks prior to imaging. All imaging sessions were conducted using medical air with 1.5\% vaporized isoflurane. All experiments were approved by the Institutional Animal Care and Use Committee (IACUC) at The University of Texas at Austin.

@@

\subsection{Laser Speckle Contrast Image Analysis}
The raw images captured by the camera were converted to speckle contrast images using Eq.~(\ref{eq:speckle_contrast}), where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) within a small region of the image. The full speckle contrast image was calculated using a 7x7-pixel sliding window centered at every pixel of the raw image and was computed, displayed, and saved in real-time using an efficient processing algorithm in custom software \cite{Tom:2008tg}.

@@

During post-processing, speckle contrast images were averaged together ($n = 45$) and converted to inverse correlation time ($\rfrac{1}{\tau_{c}}$) to provide a more quantitative measure of blood flow \cite{Briers:2001hy}. The observed speckle contrast value ($K$) was fitted for its corresponding correlation time ($\tau_{c}$) at each pixel using Eq.~(\ref{eq:bandyopadhyay}), where $x = \rfrac{T}{\tau_{c}}$ \cite{Bandyopadhyay:2005bg}. $T$ is the camera exposure duration (5 ms) and $\beta$ is an instrumentation factor that accounts for speckle sampling, polarization, and coherence effects.

@@

Each inverse correlation time sequence was then baselined against the first frame to calculate an estimate of relative change in blood flow ($rCFB = \rfrac{\tau_{c,initial}}{\tau_{c,current}}$) \cite{Kazmi:2015du}. Because $\beta$ is a property of the instrumentation and should not vary throughout the course of an experiment, it was assumed $\beta = 1$. The same regions of interest defined for DMD structured illumination were then used to calculate timecourses of the relative change in flow.

@@

\subsection{Oxygen Tension Measurements}
Oxyphor PtG4 is an oxygen-sensitive dendritic probe that contains Platinum(II)-meso-tetra-(3,5-dicarboxyphenyl)tetrabenzoporphyrin as the phosphorescent core \cite{Lebedev:2009cf,Esipova:2011hi} and has been effectively used to measure absolute oxygen tension using phosphorescence quenching \cite{Zhang:2013cd,Holt:2014cy}. It has excitation maxima near 435 nm and 623 nm and an emission maximum at 782 nm (Fig.~\ref{fig:oxyphor_ptg4}a). Unlike previous generations of the Oxyphor probe, PtG4 is highly soluble in an aqueous environment without requiring the presence of environmental albumin for stabilization \cite{Esipova:2011hi}. For \textit{in vivo} measurements, Oxyphor PtG4 was introduced systemically via retro-orbital injection into the venous sinus for a target blood plasma concentration of 5 $\mu$M. Phosphorescence lifetime measurements were made in the time domain using the structured pulsed excitation light paradigm described above. The instrument response was accounted for by introducing a 2 $\mu$s temporal offset to the phosphorescent signal [$I(t)$] prior to fitting for the decay lifetime ($\tau$) in Eq.~(\ref{eq:phosphorescence}).

% Equation 3 - Phosphorescence Decay Equation
\begin{equation}
    \label{eq:phosphorescence}
    I(t) = A + Be^{-\rfrac{t}{\tau}}
\end{equation}

@@

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). For $\tau < 16$ $\mu$s, Stern-Volmer kinetics were assumed with $k_q = 291.014$ mmHg$^{-1}$ s$^{-1}$ and $\tau_0 = 47$ $\mu$s. (c) Averaged phosphorescent decay curves ($n = 200$) in anoxic and normoxic cuvette environments with fitted lifetimes and their corresponding \pO\ values. (d) \pO\ measurements did not vary with excitation wavelength.
    }
\end{figure}

@@

\subsection{Hyperoxic Challenge}
In order to demonstrate the ability to detect systemic changes in oxygen tension, mice were subjected to a hyperoxic challenge. The oxygen fraction of inspired air under anesthesia was increased from 21\% (normoxia) to 100\% and then decreased back to 21\% for recovery. Hyperoxia was maintained for five minutes and vascular \pO\ measurements were acquired at the end of each stage. Pulse oximetry was used to monitor the status of the animal throughout the hyperoxic challenge.

@@

\subsection{Targeted Photothrombosis}
The DMD was also used to induce arbitrarily-shaped photothrombotic occlusions in the cortical vasculature using rose bengal. Rose bengal is a fast-clearing photothrombotic agent that photochemically triggers localized clot formation upon irradiation with green light \cite{Watson:1985bp,Klaassen:1976kg,Wilson:1991tv}. Structured illumination with the DMD allows for the selective targeting of individual vessels for occlusion while minimizing exposure in the surrounding parenchyma. Rose bengal was injected intravenously (50 $\mu$L, 15 mg/mL) and the target vessels exposed to DMD-patterned 532 nm laser light for 5 - 10 minutes. Descending arterioles were the primary targets because they serve as bottlenecks in the cortical oxygen supply \cite{Nishimura:2007hk}. Oxygen tension measurements were restricted when performing photothrombosis to the region being targeted for occlusion. Real-time LSCI was used to monitor clot formation within the targeted area and control the progression of the occlusion.

@@

\subsection{Excitation Wavelength Dependence of Measured Oxygen Tension}
Static oxygen tension measurements in the neurovasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The calculated \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). Despite differences in absolute value, similar trends can be seen between each of the targeted regions with both excitation wavelengths. As shown previously in Fig.~\ref{fig:oxyphor_ptg4}d, no differences in \pO\ were observed between the two wavelengths in cuvette samples.

In order to obtain a more comprehensive look at vascular oxygenation within the LSCI field of view, an array of 12x8 rectangular tiles was sequentially projected. The tiles were displayed at 10 Hz with 200 decays averaged per pattern for a total acquisition time of 9.6 seconds. The resulting \pO\ maps (Fig.~\ref{fig:static_oxygen}c, d) coarsely follow the visible surface vasculature. As expected, the large branching vein has lower \pO\ values compared to the descending arteriole approaching from the bottom or the surrounding parenchyma. 445 nm excitation again results in a wider range of \pO\ values (45 - 85 mmHg) compared to 637 nm excitation (81 - 85 mmHg).

@@

% Figure 4 - Hyperoxic Challenge
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure4.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:hyperoxic_challenge}
        Scale bar = 1 mm. (a) Speckle contrast image depicting three regions (arteriole, venule, and parenchyma) targeted for 445 nm oxygen tension measurements during an hyperoxic challenge. (b) Static \pO\ during baseline, hyperoxic, and recovery stages for each of the targeted vessels (mean $\pm$ s.d.).
    }
\end{figure}

@@

\subsection{Oxygen Tension and Blood Flow during Photothrombosis}
Targeted photothrombosis within a descending arteriole can be seen in the series of speckle contrast images in Fig.~\ref{fig:photothrombosis}a. The red overlay in the first frame depicts the 0.09 mm$^{2}$ region illuminated with DMD-targeted 532 nm light for 420 seconds. Because Oxyphor PtG4 has minimal absorbance of green light (Fig.~\ref{fig:oxyphor_ptg4}a), \pO\ measurements using 445 nm excitation were simultaneously acquired from the same region. The remaining frames depict the progression of the photothrombotic occlusion as the targeted vessel undergoes stenosis and flow is significantly reduced. After two minutes of exposure, the occluded area is indistinguishable from the surrounding parenchyma.

@@

Both relative blood flow and \pO\ decreased over the remainder of the imaging session across all regions but the targeted arteriole. At $t = 860$ s, the vessel partially reperfused, causing a sudden increase in both relative blood flow (+6 percentage points) and \pO\ (+15 mmHg). By the end of the imaging session, relative blood flow had increased to 55\% of baseline and \pO\ to 42 mmHg, likely indicated further vessel reperfusion.

% Figure 5 - Photothrombosis
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure5.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:photothrombosis}
        Scale bars = 1 mm. (a) Speckle contrast images depicting the occlusion of a descending arteriole using DMD-targeted photothrombosis (Video 1, MPEG4, XX MB). The red overlay indicates the 0.09 mm$^{2}$ region simultaneously illuminated for occlusion and \pO\ measurements. (b) Two arterioles (A1, A2), one vein (V1), and two parenchyma regions (P1, P2) were targeted for \pO\ measurements after stroke induction. (c) Relative blood flow and \pO\ within the targeted regions during and after photothrombosis. The green-shaded section indicates irradiation of the targeted arteriole. The arrow indicates the propagation of an ischemia-induced depolarization event.
    }
\end{figure}

@@

The chronic progression of the ischemia was tracked for eight days following photothrombosis. The perfusion of the occluded arteriole and broader effect on cortical flow was tracked using LSCI as shown in Fig.~\ref{fig:chronic}a. Tiled \pO\ maps acquired using both 445 nm and 637 nm excitation reveal the spatial extent of the oxygen deficit (Fig.~\ref{fig:chronic}b, c). The same five regions used during photothrombosis were targeted for chronic relative blood flow and \pO\ measurements (Fig.~\ref{fig:chronic}d-f). Relative blood flow was baselined against the pre-stroke (Day -0) measurements.

The first post-stroke measurements (Day +0) were taken immediately after the induction of photothrombosis and reveal global deficits in both blood flow and \pO. Over the next two days, the targeted arteriole partially reperfused and the infarct was localized to the surrounding area. By Day +5, the vessel fully reperfused and \pO\ measurements returned to near baseline levels.

@@

The combination of laser speckle contrast imaging and phosphorescence lifetime imaging is a purely optical, non-contact strategy for measuring blood flow and oxygen tension within the cortex. This system builds upon prior work that used structured illumination to overcome traditional limitations of lifetime imaging \cite{Ponticorvo:2010uv}. Spatially patterning excitation light with a DMD allows for the use of a point detector, which offers both high sensitivity and temporal resolution for the detection of the phosphorescence. Functionally, the spatial and temporal resolution of the system are limited by the signal-to-noise. Regions as small as 0.01 mm$^{2}$ can reliably be excited at a pattern repetition rate of 10 Hz with 200 phosphorescence decay curves collected and averaged per pattern. Because intensity of the excitation light scales with the size of the target area, larger regions could allow for faster pattern rates at the expense of averaging (e.g. 100Hz with 20-decay averaging). However, a 10 Hz pattern rate is more than sufficient for visualizing dynamic physiological events such as depolarizations, which have been reported to spread spatially at a rate of several millimeters-per-minute \cite{Lauritzen:1994vs}.

>>>>

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
We present a dual-modality imaging system combining laser speckle contrast imaging and phosphorescence lifetime quenching to simultaneously map cortical blood flow and oxygen tension (\pO) in mice. Phosphorescence signal localization is achieved through the use of a digital micromirror device (DMD) that allows for selective excitation of arbitrary regions of interest. By targeting both excitation maxima of the oxygen-sensitive porphyrin Oxyphor PtG4, we are able to examine the effects of excitation wavelength and penetration depth on phosphorescence lifetime. We demonstrate the ability to measure differences in \pO\ between arteries and veins and large changes during an hyperoxic challenge. We dynamically monitor blood flow and \pO\ during DMD-targeted photothrombotic occlusion of an arteriole and highlight the presence of an ischemia-induced depolarization. Chronic tracking of the ischemic lesion over eight days revealed a rapid recovery, with the targeted vessel fully reperfusing and \pO\ returning to baseline values within five days. This system has broad applications for studying the acute and chronic pathophysiology of ischemic stroke and other vascular diseases of the brain.
\end{abstract}

@@

\subsection{Imaging Instrumentation}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_schematic}a. LSCI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs) illuminating the craniotomy at an oblique angle. The excitation and emission spectra of the phosphorescent probe dictated dichroic beamsplitter cutoff wavelengths and limited the options for the near-infrared laser diode wavelength. The scattered light was relayed to a CMOS camera (acA1300-60gmNIR, 1280 x 1024 pixels, Basler AG) with 2x magnification for a field of view of 3.5 mm x 2.8 mm. Images were acquired using custom software written in C++ at 60 frames per second with a 5 ms exposure time.

@@

Simultaneously, laser light patterned by the DMD was delivered to the craniotomy to selectively excite the phosphorescent probe. Wavelength has been shown to significantly affect the penetration depth and sampled volume of measurements through surface vasculature \cite{Davis:2011wj}, so two different lasers at 445 nm (200 mW, AixiZ) and 637 nm (250 mW, HL6388MG, Thorlabs) were selected to target the Soret and Q band excitation maxima of the dye \cite{Esipova:2011hi}. Each laser was used independently to collect lifetime measurements from identical regions of interest for comparison. The 445 nm laser was gated using an acousto-optic modulator (23080-2-LTD, Neos Technologies) while the 637 nm laser was directly gated via its driver (LDD400-1P, Wavelength Electronics). Both lasers were gated to produce 20 $\mu$s pulses of light for time domain lifetime measurements with a 6\% duty cycle and approximately 3 kHz repetition rate using an National Instruments FlexRIO FPGA (NI PXIe-7965R and NI 5781) for waveform generation.

The modulated laser light was relayed to a DMD for projection onto the craniotomy. A DMD is an optical semiconductor device that consists of a two-dimensional array of thousands of individually addressable mirrors that can be tilted to spatially modulate light. The DMD allows for the localization of phosphorescence measurements while maintaining the high sensitivity of using a point detector \cite{Ponticorvo:2010uv}. A DLP LightCrafter Evaluation Module (Texas Instruments) was modified to expose the bare DMD (DLP3000, 608 x 684 pixels, 7.6 $\mu$m pitch) for illumination. The projected DMD pattern was co-registered with the LSCI camera via an affine image transformation (Fig.~\ref{fig:system_schematic}b). This allowed for the selection of arbitrarily-shaped regions of interest using speckle contrast imagery for guidance. The resulting binary masks were then transformed into DMD coordinate space and uploaded onto the device via its USB-based API. Each pattern was then projected sequentially onto the exposed brain tissue to selectively excite the phosphorescent probe for \pO\ measurements.

The emitted phosphorescence was separated from the excitation light and LSCI laser using a pair of dichroic beamsplitters (650 nm, ZT640rdc, Chroma Technology and 750 nm, FF750-SDi02, Semrock) and a bandpass filter (775$\pm$26 nm, 84-106, Edmund Optics) and relayed to a photomultiplier tube for detection (H7422P-50, Hamamatsu Photonics). The analog signal was digitized at 100 MHz and accumulated by the FPGA for averaging, after which it was transferred to the host computer and written to file. The maximum pattern projection rate and temporal resolution of the \pO\ measurements were limited by the averaging of the phosphorescent decays. In order to balance the signal-to-noise ratio and speed, patterns were displayed at 10 Hz with 200 decays collected during each projection. While faster pattern rates were possible (e.g. 50 Hz with 40 decays averaged), the reduction in averaging negatively affected the quality of the recorded decays.

@@

\subsection{Animal Preparation}
Mice (CD-1, male, 25-30 g, Charles River) were anesthetized with medical air vaporized isoflurane (2\%) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts). Arterial oxygen saturation, heart rate, and breath rate were monitored via pulse oximetry (MouseOx, Starr Life Sciences). After induction, mice were placed supine in a stereotaxic frame (Narishige Scientific Instrument Lab) and administered carprofen (5 mg/kg, subcutaneous) and dexamethasone (2 mg/kg, intramuscular) to reduce inflammation of the brain during the craniotomy procedure. The scalp was shaved and resected to expose skull between the bregma and lambda cranial coordinates. A thin layer of cyanoacrylate (Vetbond, 3M) was applied to the exposed skull to facilitate the adhesion of dental cement during a later step. A 3-4 mm diameter portion of the skull was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools) under regular artificial cerebrospinal fluid perfusion. A 5-8 mm round cover glass (\#1.5, World Precision Instruments) was placed over the exposed brain with a layer of artificial cerebrospinal fluid between the two. While applying gentle pressure to the cover glass, a dental cement mixture was deposited along the perimeter, bonding it to the surrounding skull. This process created a sterile, air-tight seal around the craniotomy and allowed for restoration of intracranial pressure. A layer of cyanoacrylate was applied over the dental cement to further seal the cranial window. Animals were allowed to recover from anesthesia and monitored for cranial window integrity and normal behavior for two weeks prior to imaging. All imaging sessions were conducted using medical air with 1.5\% vaporized isoflurane. The Institutional Animal Care and Use Committee at The University of Texas at Austin approved of all experiments.

@@

\subsection{Laser Speckle Contrast Image Analysis}
The raw images captured by the camera were converted to speckle contrast images using Eq.~(\ref{eq:speckle_contrast}), where speckle contrast ($K$) is defined as the ratio of the standard deviation ($\sigma_{s}$) to the mean intensity ($\langle{I}\rangle$) within a small region of the image. The full speckle contrast image was calculated using a 7x7-pixel sliding window centered at every pixel of the raw image and was computed, displayed, and saved in real-time using an efficient processing algorithm \cite{Tom:2008tg}.

@@

During post-processing, speckle contrast images were averaged together ($n = 45$) and converted to inverse correlation time ($1 / \tau_c$) images to provide a more quantitative measure of blood flow \cite{Briers:2001hy}. The observed speckle contrast ($K$) was fitted for its corresponding correlation time ($\tau_{c}$) at each pixel using Eq.~(\ref{eq:bandyopadhyay}), where $x = T / \tau_c$ \cite{Bandyopadhyay:2005bg}. $T$ is the camera exposure duration (5 ms) and $\beta$ is an instrumentation factor that accounts for speckle sampling, polarization, and coherence effects.

@@

Each inverse correlation time image was then baselined against the first frame to calculate an estimate of relative change in blood flow ($rCFB = \tau_{c,initial}/\tau_c$) \cite{Kazmi:2015du}. Because $\beta$ is a property of the instrumentation and should not vary throughout the course of an experiment, it was assumed $\beta = 1$. The same regions of interest defined for DMD structured illumination were used to calculate timecourses of the relative change in flow.

@@

\subsection{Oxygen Tension Measurements}
Oxyphor PtG4 is an oxygen-sensitive dendritic probe that contains Platinum(II)-meso-tetra-(3,5-dicarboxyphenyl)tetrabenzoporphyrin as the phosphorescent core \cite{Lebedev:2009cf,Esipova:2011hi} and has been effectively used to measure absolute oxygen tension using phosphorescence quenching \cite{Zhang:2013cd,Holt:2014cy}. It has two excitation maxima near 435 nm and 623 nm and an emission maximum at 782 nm (Fig.~\ref{fig:oxyphor_ptg4}a). Unlike previous generations of the Oxyphor probe, PtG4 is highly soluble in an aqueous environment without requiring the presence of environmental albumin for stabilization \cite{Esipova:2011hi}. For \textit{in vivo} measurements, Oxyphor PtG4 was introduced systemically via retro-orbital injection into the venous sinus for a target blood plasma concentration of 5 $\mu$M. Phosphorescence lifetime measurements were made in the time domain using the structured pulsed excitation light paradigm described above. The instrument response was accounted for by introducing a 2 $\mu$s temporal offset to the phosphorescent signal [$I(t)$] prior to fitting for the decay lifetime ($\tau$) in Eq.~(\ref{eq:phosphorescence}).

% Equation 3 - Phosphorescence Decay Equation
\begin{equation}
    \label{eq:phosphorescence}
    I(t) = A + Be^{-t / \tau}
\end{equation}

@@

% Figure 2 - Oxyphor PtG4
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:oxyphor_ptg4}
        (a) Excitation and emission spectra for Oxyphor PtG4. Dashed vertical lines indicate excitation lasers at 445 nm and 637 nm. (b) Calibration curve relating \pO\ to the measured phosphorescence lifetime ($\tau$) under physiological conditions (37 $^\circ$C, pH 7.2). For $\tau < 16$ $\mu$s, Stern-Volmer kinetics were assumed with $k_q = 291.014$ mmHg$^{-1}$ s$^{-1}$ and $\tau_0 = 47$ $\mu$s. (c) Averaged phosphorescent decay curves ($n = 200$) in anoxic and normoxic cuvette environments with fitted lifetimes and their corresponding \pO\ values. (d) Excitation wavelength does not affect measured \pO.
    }
\end{figure}

@@

\subsection{Hyperoxic Challenge}
Detection of systemic changes in oxygen tension was demonstrated by subjecting mice to a hyperoxic challenge. The oxygen fraction of inspired air under anesthesia was increased from 21\% (normoxia) to 100\% and then decreased back to normoxia for recovery. Hyperoxia was maintained for five minutes and vascular \pO\ measurements were acquired at the end of each stage. Pulse oximetry was used to monitor the status of the animal throughout the hyperoxic challenge.

@@

\subsection{Targeted Photothrombosis}
The DMD was also used to induce arbitrarily-shaped photothrombotic occlusions in the cortical vasculature using rose bengal. Rose bengal is a fast-clearing photothrombotic agent that photochemically triggers localized clot formation upon irradiation with green light \cite{Watson:1985bp,Klaassen:1976kg,Wilson:1991tv}. Structured illumination with the DMD allows for the selective targeting of individual vessels for occlusion while minimizing exposure in the surrounding parenchyma. Rose bengal was injected intravenously (50 $\mu$L, 15 mg/mL) and the target vessels exposed to DMD-patterned 532 nm laser light for 5 - 10 minutes. Descending arterioles were the primary targets because they serve as bottlenecks in the cortical oxygen supply \cite{Nishimura:2007hk}. Oxygen tension measurements were restricted when performing photothrombosis to the region being targeted for occlusion. LSCI was used to monitor clot formation within the targeted area and control the progression of the occlusion.

@@

\subsection{Excitation Wavelength Dependence of Measured Oxygen Tension}
Static oxygen tension measurements in the vasculature of the mouse cortex are shown in Fig. 3. Five different regions including two arterioles, two veins, and an area of unresolvable vasculature (parenchyma) were targeted for selective illumination using both the 445 nm and 637 nm excitation lasers (Fig.~\ref{fig:static_oxygen}a). The measured \pO\ within each region aligns well with physiological expectations as both arterioles have higher \pO\ than the venous or parenchymal areas (Fig.~\ref{fig:static_oxygen}b). The effects of wavelength can be seen as 445 nm excitation resulted in a broader range of oxygen tension values (48 - 83 mmHg) compared to 637 nm excitation (75 - 82 mmHg). Despite differences in absolute value, similar trends exist between each of the targeted regions for both excitation wavelengths. As shown previously in Fig.~\ref{fig:oxyphor_ptg4}d, no differences in \pO\ were observed between the two wavelengths in cuvette samples.

In order to obtain a more comprehensive look at vascular oxygenation within the LSCI field of view, an array of 12x8 rectangular tiles was sequentially projected. The tiles were displayed at 10 Hz with 200 decays averaged per pattern for a total acquisition time of 9.6 seconds. The resulting \pO\ maps (Fig.~\ref{fig:static_oxygen}c, d) coarsely follow the visible surface vasculature. As expected, the large branching vein has lower \pO\ values compared to the arteriole approaching from the bottom or the surrounding parenchyma. 445 nm excitation again resulted in a wider range of \pO\ values (45 - 85 mmHg) compared to 637 nm excitation (81 - 85 mmHg).

@@

% Figure 4 - Hyperoxic Challenge
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure4.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:hyperoxic_challenge}
        Scale bar = 1 mm. (a) Speckle contrast image depicting three regions (arteriole, venule, and parenchyma) targeted for 445 nm \pO\ measurements during an hyperoxic challenge. (b) Static \pO\ during baseline, hyperoxic, and recovery stages for each of the targeted vessels (mean $\pm$ s.d.).
    }
\end{figure}

@@

\subsection{Oxygen Tension and Blood Flow during Photothrombosis}
Targeted photothrombosis within a descending arteriole can be seen in the series of speckle contrast images in Fig.~\ref{fig:photothrombosis}a. The red overlay in the first frame depicts the 0.09 mm$^{2}$ region illuminated with DMD-targeted 532 nm light for 420 seconds. Because Oxyphor PtG4 has minimal absorbance of green light (Fig.~\ref{fig:oxyphor_ptg4}a), \pO\ measurements using 445 nm excitation were simultaneously acquired from the same region. The remaining frames depict the progression of the photothrombotic occlusion as the targeted vessel underwent stenosis and flow was significantly reduced. After two minutes of exposure, the occluded area was indistinguishable from the surrounding parenchyma.

@@

Both relative blood flow and \pO\ decreased over the remainder of the imaging session across all regions but the targeted arteriole. At $t = 860$ s, the vessel partially reperfused, causing a sudden increase in both relative blood flow (+6 percentage points) and \pO\ (+15 mmHg). By the end of the imaging session, relative blood flow had increased to 55\% of baseline and \pO\ to 42 mmHg, likely indicating further vessel reperfusion.

% Figure 5 - Photothrombosis
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure5.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:photothrombosis}
        Scale bars = 1 mm. (a) Speckle contrast images depicting the occlusion of a descending arteriole using DMD-targeted photothrombosis (Video 1, MPEG4, 16.9 MB). The red overlay indicates the 0.09 mm$^{2}$ region simultaneously illuminated for occlusion and \pO\ measurements. (b) Two arterioles (A1, A2), one vein (V1), and two parenchyma regions (P1, P2) were targeted for \pO\ measurements after stroke induction. (c) Relative blood flow and \pO\ within the targeted regions during and after photothrombosis. The green-shaded section indicates irradiation of the targeted arteriole. The arrow indicates the propagation of an ischemia-induced depolarization event.
    }
\end{figure}

@@

The chronic progression of the ischemia was tracked for eight days following photothrombosis. The perfusion of the occluded arteriole and broader effect on cortical flow was tracked using LSCI as shown in Fig.~\ref{fig:chronic}a. Tiled \pO\ maps acquired using both 445 nm and 637 nm excitation reveal the spatial extent of the oxygen deficit (Fig.~\ref{fig:chronic}b, c). The same five regions used during photothrombosis were targeted for chronic relative blood flow and \pO\ measurements (Fig.~\ref{fig:chronic}d-f). Relative blood flow was calculated using the pre-stroke (Day -0) measurements as baseline.

The first post-stroke measurements (Day +0) were taken immediately after the induction of photothrombosis and revealed global deficits in both blood flow and \pO. Over the next two days, the targeted arteriole partially reperfused and the infarct was localized to the surrounding area. By Day +5, the vessel had fully reperfused and \pO\ measurements returned to near baseline levels.

@@

The combination of laser speckle contrast imaging and phosphorescence lifetime imaging is a purely optical, non-contact strategy for measuring blood flow and oxygen tension within the cortex. This system builds upon prior work that used structured illumination to overcome traditional limitations of lifetime imaging \cite{Ponticorvo:2010uv}. Spatially patterning excitation light with a DMD allows for the use of a point detector, which offers both high sensitivity and speed for the collection of the phosphorescent signal. The spatial and temporal resolutions of the system are ultimately limited by noise. Regions as small as 0.01 mm$^{2}$ can reliably be excited at a pattern repetition rate of 10 Hz with 200 phosphorescent decays collected and averaged per pattern. Because intensity of the excitation light scales with the size of the target area, larger regions could allow for faster pattern rates at the expense of averaging (e.g. 100 Hz with 20-decay averaging). However, a 10 Hz pattern rate is more than sufficient for visualizing dynamic physiological events such as spreading depolarizations, which have been reported to propagate at a rate of several millimeters per minute \cite{Lauritzen:1994vs}.
